### 2014-01-30 inst/examples/Reed.Rmd
Beverton Holt example

`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
````

@@

``` {r }
f <- RickerAllee
K <- 10
pars <- c(2, K, 5)
````

@@

``` {r noise}
z_g <- function() 1 + rlnorm(1,0, sigma_g)  
pdfn <- function(P, s) dlnorm(P, 0, s)

@@

``` {r  SDP_Mat}
p <- c(.2,7.5,5)
SDP_Mat <- determine_SDP_matrix(f, p, x_grid, h_grid, sigma_g, pdfn)
````

@@

``` {r policyfn_plot}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]], Stationary = x_grid[s_opt$D]), id="stock")
q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point(alpha=.5) + xlab("stock size") + ylab("escapement") 
q1
````

>>>>

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE)
````

@@

``` {r }
#f <- RickerAllee
#pars <- c(2, K, 5)
f <- BevHolt
pars <- c(2,4)
K <- (pars[1]-1)/pars[2]

#K <- 100
#pars <- c(1,K)
#f <- function(x,h,p){
#  sapply(x, function(x){
 #   S = max(x - h, 0)
#    p[1] * S * (1 - S/p[2]) + S
#  })
#}

````

@@

``` {r noise}
#z_g <- function() 1 + rlnorm(1,0, sigma_g)  
pdfn <- function(P, s) dlnorm(P, 0, s)

@@

``` {r  SDP_Mat}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

@@

``` {r policyfn_plot}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, 
                            S = x_grid[opt$D[,1]], 
                            D = x_grid[det$D[,1]], 
                            Stationary = x_grid[s_opt$D]
                            ), id="stock")
q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point(alpha=.4) + xlab("stock size") + ylab("escapement") 
q1
````
